### 2016-11-15 paper/intro.tex
pass on intro

As software evolves it is expected that the number of tests and the
length of test runs increase.  Both elements can add up to the
aggregate cost of running a test suite, which can lead to late reports
of test failures.  At large IT organizations, dealing with high
testing costs is a common problem.  The Google TAP
system~\cite{google-tap,google-ci} and the Microsoft CloudBuild
system~\cite{prasad-shulte-ieee-microsoft-ci} provide evidence about
the importance of speeding up test execution in industry.  This
problem is not specific for giants like Microsoft and Google; it also
occur in other domains.  For example, a recent paper from the
automotive industry reported that test suites can take days to
run~\cite{artl-etal-icst2015}.

@@

Several approaches have been proposed in the literature to optimize
regression testing.  Research has focused mostly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  Although regression testing is
a recognized problem in academia and at large organizations, to the
best of our knowledge no prior work has investigated how prevalent the
problem is in open-source projects.  In large organizations, the
alternative of renting a cloud
service\footnote{\url{https://clutch.co/cloud}}, or even building a
server farm (for increased security), is a potential escape to the
regression testing problem.  Considering open-source projects and
lower-budget projects, the alternative of building or using high-end
infrastructures is not as attractive but it is unclear how relevant
regression testing is in this scenario.

@@

Motivated by this potential gap in regression testing, we studied (1)
how prevalent long-running test suites are in open-source software
projects.  To conduct this experiment we selected \numSubjs{} Java
projects from github that are highly-popular and use the Maven build
system.  (Section~\ref{sec:eval} details our selection methodology.)
Our experimental results indicate that long-running test suites
(taking longer than 5m to complete\Fix{check if Ekstazi paper also
  used this value to indicate long runs and cite}) are not
rare~--~\numLongRunning{} of the projects we analyzed contain
long-running test suites.  \Mar{missing connection. why parallelism?}
From this result we investigated (2) how frequently the projects we
considered use parallelization to speedup test runs.  Our results
indicate that \percentParallelForLongRunning{} of long-running test
suites do use parallelism to speedup execution.  Given the popularity
of this solution, we further studied: (3) what are the causes of high
execution cost in individual tests (CPU vs. IO) and (4) how uniformly
cost is distributed across tests.  These questions help to assess the
impact of parallelization in test suite execution.  Intuitively,
IO-intensive test suites and test suites with uneven distribution of
cost per test are factors that limit the benefits of parallelization.
Results indicate that \Fix{...}  Finally, we investigated (5) what are
the limitations related to parallelization that could justify adoption
resistance.

@@

%%  LocalWords:  parallelization multicore JUnit TestNG NUnit XXm YYm
%%  LocalWords:  Groupon parallelizing multi JVMs CPUs JVM Milos TODO
%%  LocalWords:  Ekstazi github CloudBuild

>>>>

As software evolves it is expected that the number of tests and the
length of test runs increase.  Both elements can add up to the
aggregate cost of running a test suite, which can lead to late reports
of test failures.  At large IT organizations, dealing with high
testing costs is a common problem.  The Google TAP
system~\cite{google-tap,google-ci} and the Microsoft CloudBuild
system~\cite{prasad-shulte-ieee-microsoft-ci} evidence the importance
of speeding up test execution in industry.  This problem, however, is
not specific to industrial giants like Microsoft and Google.  For
example, a recent paper from the automotive industry reported that
test suites can take days to run~\cite{artl-etal-icst2015}.

@@

Several approaches have been proposed in the literature to optimize
regression testing.  Research has focused mostly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  Although regression testing is
a recognized problem both in industry and academia, to the best of our
knowledge no prior work has investigated how prevalent the problem is
in open-source projects.  Renting a cloud
service\footnote{\url{https://clutch.co/cloud}}, or even building a
server farm (for increased security), is a popular approach to
mitigate the regression testing problem in large organizations.  This
alternative can be used irrespective of complementary approaches to
save testing costs (e.g., test selection).  For example, as of August
2013, the Groupon PWA system, which powers the \url{groupon.com}
website, included over 19K tests.  To run all those tests, Groupon
used a cluster of 4 computers with 24 cores
each~\cite{kim-etal-fse2013}.  This approach, however, is unlikely to
be attractive for open-source and lower-budget projects.

@@

%Motivated by this potential gap in regression testing,

This paper focuses on the problem of understanding how critical the
regression testing problem is in open-source projects and what are the
potential benefits and shortcomings of using the parallelization
features of build systems and testing frameworks, which are very
popular today\Fix{cite cite cite}.  More precisely, we studied (1) how
prevalent long-running test suites are in open-source software
projects.  To conduct this experiment we selected \numSubjs{} Java
projects from github that are highly-popular and use the Maven build
system.  (Section~\ref{sec:eval} details our selection methodology.)
Our experimental results indicate that long-running test suites
(taking longer than 5m to complete\Fix{check if Ekstazi paper also
  used this value to indicate long runs and cite}) are not
rare~--~\numLongRunning{} of the projects we analyzed contain
long-running test suites.  \Mar{missing connection. why parallelism?}
From this result we investigated (2) how frequently the projects we
considered use parallelization to speedup test runs.  Our results
indicate that \percentParallelForLongRunning{} of long-running test
suites do use parallelism to speedup execution.  Given the popularity
of this solution, we further studied: (3) what are the causes of high
execution cost in individual tests (CPU vs. IO) and (4) how uniformly
cost is distributed across tests.  These questions help to assess the
impact of parallelization in test suite execution.  Intuitively,
IO-intensive test suites and test suites with uneven distribution of
cost per test are factors that limit the benefits of parallelization.
Results indicate that \Fix{...}  Finally, we investigated (5) what are
the limitations related to parallelization that could justify adoption
resistance.

@@

%%  LocalWords:  parallelization multicore JUnit TestNG NUnit XXm YYm
%%  LocalWords:  Groupon parallelizing multi JVMs CPUs JVM Milos TODO
%%  LocalWords:  Ekstazi github CloudBuild PWA groupon
